New lower bounds for Schur and weak Schur numbers

### 2021-09-21 article/schur.tex
modifs + numerotation cassee :'(

We begin by introducing \textit{S-templates}, standing for \textit{"Schur templates"}. The idea is to consider the first line
of \hyperref[figure:1]{Figure 1} not as a combination of two blocs anymore but as a whole, single construction. We thereby define a S-template as
a new object filling the role of the first line but with less, yet sufficiant, constraints that will allow the expansion of the
table.

@@

\begin{remark}
	\(S^+\) and \(S\) have the same asymptotic growth rate.
\end{remark}

>>>>

We begin by introducing \textit{S-templates}, standing for \textit{"Schur templates"}. The idea is to consider the first line
of \hyperref[figure:1]{Figure 1} not as a combination of two blocs anymore but as a whole, single construction. A S-template 
is then defined as a new object filling the role of the first line but with less, yet sufficiant, constraints which allow a linear 
expansion of the partition.

@@

### 2021-09-21 article/weakschur.tex
modifs + numerotation cassee :'(

\qquad In this section, we generalize Rowley's constructions for weak Schur numbers \cite{RowleyWS} and give an analogous
for weak Schur numbers of Abbott and Hanson's construction for Schur numbers. By analogy with the previous section,
we then introduce WS-templates as well as an associated sequence \(\WS^+(n)\). We find templates and use them to
provide new lower bounds for weak Schur numbers. Finally, we give a short explanation for the new lower bound 
\(\WS(6) \geqslant 646\) which was not directly obtained with a template contrary to the other lower bounds given in this 
paper.

@@

\begin{remark}
\(\WS^+\) and \(\WS\) have the same asymptotic growth rate.
\end{remark}

@@

>>>>

\qquad In this section, we generalize Rowley's constructions for weak Schur numbers \cite{RowleyWS} and give an analogous
for weak Schur numbers of Abbott and Hanson's construction for Schur numbers. By analogy with the previous section,
we then introduce WS-templates, standing for \textit{"weak Schur templates"}, as well as an associated sequence \(\WS^+(n)\). 
We find templates and use them to provide new lower bounds for weak Schur numbers. Finally, we give a short explanation for 
the new lower bound \(\WS(6) \geqslant 646\) which was not directly obtained with a template contrary to the other lower bounds 
given in this paper.

@@

@@

Theorem provides a way to extend a S-template into a larger Schur partitions using other Schur partitions. Likewise, a WS-template can 
be extended into larger weak Schur partitions in using Schur partitions. This is the object of the following theorem.
